The Stakes of Scrying: \\ \lstinline[style=inlinecode]{.^} dotket and the Seer Proposal

### 2024-04-27 mss.tex
Fix typo

While Nock formally has twelve opcodes, numbered 0--11, it is convenient to expose in userspace a fake Nock 12 opcode to expose the scry namespace to userspace developers without an asynchronous retrievel step.  This opcode is trivially invoked by using the Hoon \dotket~rune.\footnote{The idea of using a pattern like scrying to introduce a value into a referentially transparent namespace predates Urbit itself; cf. \citet{Yarvin2006}.}  However, Nock 12 breaks the referential transparency of Nock, and this has consequences for the purity of Urbit's functional programming model.

>>>>

While Nock formally has twelve opcodes, numbered 0--11, it is convenient to expose in userspace a fake Nock 12 opcode to expose the scry namespace to userspace developers without an asynchronous retrieval step.  This opcode is trivially invoked by using the Hoon \dotket~rune.\footnote{The idea of using a pattern like scrying to introduce a value into a referentially transparent namespace predates Urbit itself; cf. \citet{Yarvin2006}.}  However, Nock 12 breaks the referential transparency of Nock, and this has consequences for the purity of Urbit's functional programming model.
